Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-12-05 prevalence_testing/postshocktest2021draft.tex
new codes for functions and data analysis and some addition to manuscript

\begin{table}[H]
	\begin{center}
		\begin{tabular}{cccccc}
  \hline
 & null & Permanent & Decay without scale & Decay with scale & Complicate \\ 
  \hline
TS2 & 239.71 & 241.70 & 241.71 & 242.91 & 236.17 \\ 
  TS3 & 276.52 & 277.73 & 272.63 & 275.79 & 274.25 \\ 
  TS4 & 215.67 & 212.55 & 214.45 & 211.37 & 198.31 \\ 
  Mean & 243.97 & 244.00 & 242.93 & 243.36 & 236.24 \\ 
  TS1 & 262.59 & 260.58 & 239.07 & 266.03 & 206.03 \\ 
   \hline
\end{tabular}
	\end{center}	
\end{table}

\begin{table}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
     \hline 
     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
      7 & Complicate & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
     15 & Decaying & 0 & & 0 & \textcolor{red}{0} & \textcolor{red}{0}   & $250.107$  \\
     15 & Complicate & 1 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  & $232.084$\\[.2cm]
     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
     30 & Complicate & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
  \end{tabular}
\end{center}	
\end{table}

>>>>

\begin{table}[H]
	\caption{Results for Cocono Philips}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$ ($T_i-T^*_i$) & Model & $p_1$ & $\mathbf{W}^*=(0,0,1)$ & $|\hat{p}-p_1|$ & Vote & weighted Vote  & weighted  AIC\\
     \hline 
     7 & Permanent & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0} & $212.554$ \\
     7 & Decaying & 0 && $0.395$ &  0 (incorrect)  & 0 (incorrect) & $214.447$ \\
      7 & Complicate & 1 && $0.090$   &  \textcolor{red}{0} & \textcolor{red}{0}  & 198.307 \\[.2cm]
     15 & Permanent & 1 &  & 0 & \textcolor{red}{0} &  \textcolor{red}{0}    & 249.637 \\
     15 & Decaying & 0 & & 0 & \textcolor{red}{1} & \textcolor{red}{1}   & $250.107$  \\
     15 & Complicate & 1 & & 0 & \textcolor{red}{0}  & \textcolor{red}{0}  & $232.084$\\[.2cm]
     30 & Permanent & 1 &  & $0$ &  \textcolor{red}{0} & \textcolor{red}{0}  &  302.089 \\
     30 & Decaying & 0 & & 0 & \textcolor{red}{1}  & \textcolor{red}{1}  &  $302.432$ \\
     30 & Complicate & 1 & & 0 & \textcolor{red}{0} &\textcolor{red}{0}  & 298.345
  \end{tabular}
\end{center}	
\end{table}
